---
title: "Reproducible Pitch: BMI"
author: "Heidi Tang"
date: "March 20, 2024"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction
- According to the World Health Organization (WHO), BMI is defined as body weight of a person in kg. divided by the square of the corresponding height in metres (kg/m2) ([WHO, 2010](https://www.who.int/europe/news-room/fact-sheets/item/a-healthy-lifestyle---who-recommendations#:~:text=Body%20mass%20index%20%2D%20BMI&text=It%20is%20defined%20as%20a,1.752%20(m2)%20%3D%2022.9%20BMI)).
- This Reproducible Pitch focuses on the calculation of BMI, given a person's height and weight.

## BMI: ui.R Code
```{r}
library(shiny)

shinyUI(fluidPage(  
    titlePanel("Shiny Application: BMI Calculation"),
    sidebarLayout(
        sidebarPanel(
          h1("Height"),
          sliderInput("ht", "Please slide to your height value in cm.", 20, 280, 0),
          h1("Weight"),
          sliderInput("wt", "Please slide to your weight value in kg.", 0.2, 650, 0)
        ),
        mainPanel(
          h3("BMI"),
          textOutput("bmi")
        )
    )
))
```

## BMI: HTML Link for Server Calculation
```{r}
library(shiny)

BMI = function(height,weight){
  return(100^2*(weight/(height)^2))
}

shinyServer(function(input, output) {
  
        output$bmi = renderText({BMI(input$ht, input$wt)})

})
```

- Link for BMI Calculation: [Click Me For Your Health!](https://heidi24.shinyapps.io/ShinyApp/)

## BMI: A Example

- If a women were 170 cm high and weighed 52 kg, then her BMI were:

   # BMI(ht=1.7m, wt=52kg) = 52/(1.7)^2 = 17.99308
